Testing Statistical Graphics

### 2022-06-25 index.qmd
Adding references and a few bits of intro

Importance of testing statistical graphics

@@

>>>>

<!-- Importance of testing statistical graphics -->

Charts and data visualizations are primary methods of communicating scientific information to the public in what we typically hope is an easy-to-digest, visually attractive package.
There are many strategies for creating charts and graphs, from Tufte-esque minimalism\cite{tufte} to charts designed with extra imagery and aesthetic appeal that draw the viewer's attention and persist in memory\cite[Ch 3]{cairoFunctionalArtIntroduction2012}. 
For a specified type of data, there are also usually many different chart forms to display that data: for instance, if we have a set of categorical data and we wish to show the relative proportions of each category, we could do so using a stacked bar chart or the polar equivalent, a pie chart. 
There have been several attempts to list out all of the types of charts\cite{ribeccaSearchChartsData}, create a taxonomy of charts\cite{bertin1983semiology}, or even to classify charts using a domain-specific grammar; the grammar of graphics\cite{wilkinsonGrammarGraphics1999}. 
With all of the different design choices available, how are chart creators to know what is the best approach for communicating data to the appropriate audience?

@@

# Monitoring the Data

Use of pilot data to set up analysis documents, github actions and/or shiny dashboard to monitor incoming results.

Not necessarily important for small tests of limited duration, because data from e.g. prolific comes in so quickly. Server load is actually a much greater concern.
